How to Analyze Build Logs---A~Comparative Study of Chunk~Retrieval~Techniques

### 2020-04-03 tse-paper/content.tex
move todos to tex

First, we filtered out articles based on 1) their title and 2) the
contextual information Google Scholar displayed.
We inlcuded only
publications written in a language intelligible to the authors (that
is, English or German), but only disregarded fewer than 1\% of search
hits due to this criterion.
Our strategy was to err on the side of
caution, that is rather including a paper than not.
We then unified
the results of the four search queries based on the link as the
identifying element, removing 60 articles that appeared in more than
one search query.
We noticed that some publishers (ACM, Springer,
Google Books) augment a link to an article with a cutomized ID, which
specifies the link source ({\tt casa\_token, oid}).
\todo{overly specific?} We automatically
removed it to find all true duplicates.
After this process, we were
left with 259 (17\%) of the original search results.

@@

\subsection{Article Classification}
Having trimmed down the set of articles, we investigated them in depth.
kept all articles that use logs from software builds as input to some
kind of process.
we wanted to characterize how researchers use buildlogs as input to
any processes.
Interesed in
\begin{itemize}
  \item what kind of build logs they are using and the source of these
  logs.
  \item what information they are retrieving from the logs,
  its kind (chunk/classification) and
  what they use the retrieved information for
  \item which technique they are using to process the build logs,
  in how much detail it is described and whether they published their
  tools
\end{itemize}
To objecifiy our data extraction we created a template of the targeted
factors
and performed a pilot on five articles.
Two authors extracted the data from the
five pilot articles and we held a consensus meeting to unify our
understanding
of the factors in the data extraction templates.
The remaining articles were
divided over these two authors.
We inspected the articles as closesly as necessary,
starting from occurences of ``log'' or ``build'' within the text.
The full data extraction template and our results of this step can be
found in
our replication package \todo{cite}.

In this pass we further identified x duplicate articles \todo{do we push
those to the last pass?}.
For several cases, multiple articles extended others, though still
reported on
the same work with the respect to analyzing build logs.
Of these we only considered the earliest article which reported on
the processing
of build logs.

@@

\subsection{Discussion}
various researchers analyzing build logs to support their research,
tools developed to help developers \todo{motivational reference}.

>>>>

First, we filtered out articles based on 1) their title and 2) the
contextual information Google Scholar displayed.
We inlcuded only
publications written in a language intelligible to the authors (that
is, English or German), but only disregarded fewer than 1\% of search
hits due to this criterion.
Our strategy was to err on the side of
caution, that is rather including a paper than not.
We then unified
the results of the four search queries based on the link as the
identifying element, removing 60 articles that appeared in more than
one search query.
We noticed that some publishers (ACM, Springer,
Google Books) augment a link to an article with a cutomized ID, which
specifies the link source ({\tt casa\_token, oid}).
% TODO: {overly specific?}
We automatically
removed it to find all true duplicates.
After this process, we were
left with 259 (17\%) of the original search results.

@@

\subsection{Article Classification}
Having trimmed down the set of articles, we investigated them in depth.
kept all articles that use logs from software builds as input to some
kind of process.
we wanted to characterize how researchers use buildlogs as input to
any processes.
Interesed in
\begin{itemize}
  \item what kind of build logs they are using and the source of these
  logs.
  \item what information they are retrieving from the logs,
  its kind (chunk/classification) and
  what they use the retrieved information for
  \item which technique they are using to process the build logs,
  in how much detail it is described and whether they published their
  tools
\end{itemize}
To objecifiy our data extraction we created a template of the targeted
factors
and performed a pilot on five articles.
Two authors extracted the data from the
five pilot articles and we held a consensus meeting to unify our
understanding
of the factors in the data extraction templates.
The remaining articles were
divided over these two authors.
We inspected the articles as closesly as necessary,
starting from occurences of ``log'' or ``build'' within the text.
The full data extraction template and our results of this step can be
found in
our replication package % TODO: {cite}.

In this pass we further identified x duplicate articles % TODO: {do we push
% those to the last pass?}.
For several cases, multiple articles extended others, though still
reported on
the same work with the respect to analyzing build logs.
Of these we only considered the earliest article which reported on
the processing
of build logs.

@@

\subsection{Discussion}
various researchers analyzing build logs to support their research,
tools developed to help developers % TODO: {motivational reference}.
